---
title: "Group-4_Project"
author: "Jamie Bigley"
date: "6/21/2021"
output: html_document
 


---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, warning = FALSE, message = FALSE)
```


# Group 4 Project

Europe's Energy Production/Consumption Review

```{r}
#Library that are used for this report
library(sqldf)
library(ggplot2)
library(reshape2)
library(tidyverse)
library(dplyr)
library(gridExtra)
library(gsubfn)
library(proto)
```


```{r}
#Load data sets for project
#Energy information from BP
bp_information <- read.csv("https://www.bp.com/content/dam/bp/business-sites/en/global/corporate/xlsx/energy-economics/statistical-review/bp-stats-review-2020-consolidated-dataset-panel-format.csv")

#World population information
World_Pop <- read.csv(file = "World_Pop.csv", header = TRUE, sep = ",")

#Countries Area information
areas <- read.csv(file = "countries_area.csv")

#GDP information
df_gdp <- read.csv(file = "API_GDP_dataframe.csv")
```


```{r}
#Prepare World Population 'World_Pop' data.frame in preparation to merge with other data.frames

#Remove all the 'X' from the column titles for the years
names(World_Pop) <- sub("^X", "", names(World_Pop))

#Rename the column of 'Country_Name' to 'Country'
names(World_Pop)[1] <- "Country"

#Need to convert each year column to a year column
World_Pop <- melt(World_Pop, id.vars = c("Country"))
World_Pop <- World_Pop[-c(1:792),]

#Need to rename the two columns year and population
names(World_Pop)[2] <- "Year"
names(World_Pop)[3] <- "Population"
```

```{r}
#Prepare Countries Area File in preparation to merge with other dataframes

#Need to clean up file by removing 3rd row
areas <- subset(areas, select = -c(3))

#Need to rename columns to 'Country' and 'Area(kms)'
names(areas)[1] <- paste("Country")
names(areas)[2] <- paste("Area(km2)")

#Need to remove the first row
areas <- areas[-c(1),]

#Need to change area(km2) to numeric vector
areas$`Area(km2)` <- as.numeric(as.character(areas$`Area(km2)`))
```

```{r}
#Prepare GDP file in preparation to merge with other dataframes

#Need to remove unneeded columns
df_gdp <- df_gdp[-c(2:4)]

#Need to rename columns
names(df_gdp)[1] <- paste("Country")
names(df_gdp) <- gsub("X", "", names(df_gdp))

#Convert each column year into a column of years and remove the "NA". 
df_gdp <- melt(df_gdp, id.vars = c("Country"))
df_gdp <- na.omit(df_gdp)

#Rename columns for year and currency
names(df_gdp)[2] <- paste("Year")
names(df_gdp)[3] <- paste("GDP.US..")

#Need to change the year to a numeric vector
df_gdp$Year <- as.numeric(as.character(df_gdp$Year))
```

```{r}
#Merging all the data.frame into one data set.

#Merge Area and GDP into a project data.frame
Project <- merge(df_gdp, areas, by = "Country")

#Now add World Population to the 'Project' dataframe
Project <- merge(Project, World_Pop, by.x = c("Country", "Year"))

#Now adding BP information to the Project dataframe
Project <- merge(Project, bp_information, by.x = c("Country", "Year"))

#Reducing the Project dataframe to just countries with a 'SubRegion' = Europe
Project <- Project[c(which(Project$SubRegion == "Europe")),]

#Some column are NA for all of Europe.  Those columns will be removed.
Project <- subset(Project, select = -c(biodiesel_cons_kbd, biodiesel_cons_kboed, biodiesel_cons_ktoe, 
                                       biodiesel_prod_kbd, biodiesel_prod_kboed, biodiesel_cons_pj, ethanol_cons_pj,
                                       biodiesel_prod_ktoe, biodiesel_prod_pj, cobalt_kt, ethanol_cons_kbd, 
                                       ethanol_cons_kboed, ethanol_cons_ktoe, ethanol_prod_kbd, ethanol_prod_kboed),)

#Remaining 'NA' are equal to zero.  Replacing all NA with 0
Project[is.na(Project)] = 0

#Correcting the units of measurement for 'biofuels'
Project$biofuels_prod_pj <- Project$biofuels_prod_pj * 0.001
names(Project)[24] <- paste("biofuels_prod_ej")
Project$biofuels_cons_pj <- Project$biofuels_cons_pj * 0.001
names(Project)[20] <- paste("biofuels_cons_ej")

#Write to complete data set to in case files change
write.csv(Project,"Project.csv")
```


```{r}
#Because of the number of countries in the Europe "SubRegion" the data set will be reduced to the countries with the highest GDP
Project_2019 <- subset(Project, Year == 2019)
TopGDP <- top_n(Project_2019, 10, GDP.US..)
TopGDP <- TopGDP$Country

Project <- Project[ Project$Country %in% TopGDP, ]
```

# Data Clean Up
Data set was reduced to Countries with the Highest GDP

Countries   Countries
---------   ---------
Belgium     France
Germany     Italy
Netherlands Poland
Spain       Switzerland
Turkey      United Kingdom

```{r}
TopGDP
```


```{r}
#Looking at renewables consumed from each Country.
#First make a new data frame with just the renewable energy source.
Total_Renew <- Project[, c("Country", "Year", "GDP.US..", "Population", 
                           "hydro_ej", "ren_power_ej", 
                           "renewables_ej","solar_ej", "wind_ej")]
Total_Renew$Total <- rowSums(Total_Renew[, 5:9])

TotalRenewPlot <- ggplot(Total_Renew, aes(x = Year, y = Total)) + geom_line(aes(color = Country))
TotalRenewPlot <- TotalRenewPlot + labs(title = "Renewables Energy", y = "Energy EJ") + theme(plot.title = element_text(hjust = 0.5))
TotalRenewPlot <- TotalRenewPlot + theme(panel.background = element_rect(fill = "light blue", 
                                                                         color = "light blue", 
                                                                         size = 0.5, 
                                                                         linetype = "solid"))
```
# Renewable Energy
```{r}
plot(TotalRenewPlot)
```

```{r}
#Looking at fossil fuels consumed from each Country.
#First make a new data frame with just the fossil fuels energy source.

Total_Fossil <- Project[ , c("Country", "Year", "GDP.US..", "Population", 
                           "biofuels_cons_ej", "biogeo_ej", "coalcons_ej",
                           "gascons_ej", "oilcons_ej", "nuclear_ej")]
Total_Fossil$Total <- rowSums(Total_Fossil[, 5:10])

TotalFossilPlot <- ggplot(Total_Fossil, aes(x = Year, y = Total)) + geom_line(aes(color = Country))
TotalFossilPlot <- TotalFossilPlot + labs(title = "Energy Consumed by Fossil Fuels", y = "Energy EJ") + 
  theme(plot.title = element_text(hjust = 0.5))
TotalFossilPlot <- TotalFossilPlot + theme(panel.background = element_rect(fill = "light blue", 
                                                                         color = "light blue", 
                                                                         size = 0.5, 
                                                                         linetype = "solid"))
```
# Fossil Fuels
```{r}
plot(TotalFossilPlot)
```

```{r}
#Next we will look at Total Energy Consumed.
#Combining the renewable and fossil data frames
TotalEnergy <- Project[ , c("Country", "Year", "GDP.US..", "Population", 
                           "biofuels_cons_ej", "biogeo_ej", "coalcons_ej",
                           "gascons_ej", "oilcons_ej", "hydro_ej", "nuclear_ej", 
                           "ren_power_ej", "renewables_ej", "solar_ej", "wind_ej")]
TotalEnergy$Total <- rowSums(TotalEnergy[ , 5:15])
TotalEnergyPlot <- ggplot(TotalEnergy, aes(x = Year, y = Total)) + geom_line(aes(color = Country))
TotalEnergyPlot <- TotalEnergyPlot + labs(title = "Total Energy Consumed", y = "Energy EJ") + 
  theme(plot.title = element_text(hjust = 0.5))
TotalEnergyPlot <- TotalEnergyPlot + theme(panel.background = element_rect(fill = "light blue", 
                                                                         color = "light blue", 
                                                                         size = 0.5, 
                                                                         linetype = "solid"))
```

# Total Energy Consumed
```{r}
plot(TotalEnergyPlot)
#Energy consumption looks pretty stable across each country.  Try comparing this information to population and land area.
```

```{r}
#First we look at energy per population
#First we need to change 'Population' to a numeric 
TotalEnergy$Population <- as.numeric(TotalEnergy$Population)

EnergyPerPopulationPlot <- ggplot(TotalEnergy, aes(x = Year, y = (Total/Population))) + 
  geom_line(aes(color = Country)) + labs(title = "Energy Consumed by Population", y = "Energy EJ") +
  theme(plot.title = element_text(hjust = 0.5)) + theme(panel.background = element_rect(fill = "light blue",
                                                                                        color = "light blue",
                                                                                        size = 0.5,
                                                                                        linetype = "solid"))
```

# Energy Consumed by Population
```{r}
plot(EnergyPerPopulationPlot)
```

```{r}
#lets but this in comparison with a population plot
PopulationPlot <- ggplot(TotalEnergy, aes(x = Year, y = Population)) + 
  geom_line(aes(color = Country)) + labs(title = "Population by Country", y = "Population") +
  theme(plot.title = element_text(hjust = 0.5)) + theme(panel.background = element_rect(fill = "light blue",
                                                                                        color = "light blue",
                                                                                        size = 0.5,
                                                                                        linetype = "solid"))
```

```{r}
#Production per population.
#Create a data.frame for energy production source.  
EnergyProductionTotal <- Project[ , c("Country", "Year", "Population", "biofuels_prod_ej", "biogeo_ej", "coalprod_ej", "gasprod_ej", "hydro_ej", "nuclear_ej", "ren_power_ej", "renewables_ej", "solar_ej", "wind_ej")]

#Create a column to sum all the energy production sources
EnergyProductionTotal$Total_Prod <- rowSums(EnergyProductionTotal[, 4:13])
EnergyProductionTotal$Population <- as.numeric(EnergyProductionTotal$Population)
 

ProductionPopulationPlot <- ggplot(EnergyProductionTotal, aes(x = Year, y = (Total_Prod/Population))) +
  geom_line(aes(color = Country)) + labs(title = "Energy Producted by Population", y = "Energy EJ") +
  theme(plot.title = element_text(hjust = 0.5)) + theme(panel.background = element_rect(fill = "light blue",
                                                                                        color = "light blue",
                                                                                        size = 0.5,
                                                                                        linetype = "solid"))

```
# Energy Produced by the Country Population
```{r}
plot(ProductionPopulationPlot)
```

# Population by Country
```{r}
plot(PopulationPlot)
```

```{r}
#Next lets look at the ratio of fossil fuels to renewable consumed.  

EnergyConRatio <- Total_Renew[, c("Country", "Year", "Population", "Total")]
names(EnergyConRatio)[4] <- paste("Renew_Total(Ej)")
EnergyConRatio$Total_Fossil <- Total_Fossil$Total
names(EnergyConRatio)[5] <- paste("Total_Fossil (Ej)")
EnergyConRatio$Renew_Fossil <- EnergyConRatio$`Renew_Total(Ej)`/EnergyConRatio$`Total_Fossil (Ej)`

#Plot the ratio for each country each year
EnergyConRatioPlot <- ggplot(EnergyConRatio, aes(x = Year, y = Renew_Fossil)) + geom_line(aes(color = Country)) +
  labs(title = "Renew/Fossil Consumed", y = "Ratio") +
  theme(plot.title = element_text(hjust = 0.5)) + theme(panel.background = element_rect(fill = "light blue",
                                                                                        color = "light blue",
                                                                                        size = 0.5,
                                                                                        linetype = "solid"))
```

# Rate of Renewable to Fossil Fuels Used
```{r}
plot(EnergyConRatioPlot)
```


```{r}
#Look at the different Energy Production based off the about of area in a country
Prod_2019 <- subset(Project, Year == 2019)
ProductionArea <- Prod_2019[, c("Country", "Area(km2)", "biofuels_prod_ej", "biogeo_ej",
                                   "coalprod_ej", "gasprod_ej", "hydro_ej", 
                                   "nuclear_ej", "ren_power_ej", "renewables_ej", "solar_ej", "wind_ej")]

ProductionArea$Total <- rowSums(ProductionArea[ , 3:12])
ProdAreaPer <- Prod_2019[, c("Country", "Area(km2)")]
ProdAreaPer$biofuelsPercent <- (ProductionArea$biofuels_prod_ej / ProductionArea$Total)*100
ProdAreaPer$biogeo_ejPercent <- (ProductionArea$biogeo_ej / ProductionArea$Total)*100
ProdAreaPer$coalprod_ejPercent <- (ProductionArea$coalprod_ej / ProductionArea$Total)*100
ProdAreaPer$gasprod_ejPercent <- (ProductionArea$gasprod_ej / ProductionArea$Total)*100
ProdAreaPer$hydro_ejPercent <- (ProductionArea$hydro_ej / ProductionArea$Total)*100
ProdAreaPer$nuclear_ejPercent <- (ProductionArea$nuclear_ej / ProductionArea$Total)*100
ProdAreaPer$ren_power_ejPercent <- (ProductionArea$ren_power_ej / ProductionArea$Total)*100
ProdAreaPer$renewables_ejPercent <- (ProductionArea$renewables_ej / ProductionArea$Total)*100
ProdAreaPer$solar_ejPercent <- (ProductionArea$solar_ej / ProductionArea$Total)*100
ProdAreaPer$wind_ejPercent <- (ProductionArea$wind_ej / ProductionArea$Total)*100
names(ProdAreaPer)[2] <- paste("Areakm2")
ProdAreaPer <- melt(ProdAreaPer, id.vars = c("Areakm2", "Country"))
ProdAreaPer$Areakm2 <- as.character(ProdAreaPer$Areakm2)

AreaPlot <- ggplot(ProdAreaPer, aes(x = Country, y = value, fill = variable)) + geom_bar(position = 'stack', stat = 'identity', color = "black") + labs(title = "Energy Production by Country", y = "Percentage %", col = "Country") + theme(axis.text.x = element_text(angle = 90)) +
  theme(plot.title = element_text(hjust = 0.5)) + theme(panel.background = element_rect(fill = "light blue",
                                                                                        color = "light blue",
                                                                                        size = 0.5,
                                                                                        linetype = "solid"))

```
# Ratio of Energy Sources from Area of Country
```{r}
plot(AreaPlot)
```

```{r}
#Look at the different Energy Production based off the about of area in a country
Prod_2019 <- subset(Project, Year == 2019)
ProductionArea <- Prod_2019[, c("Country", "Area(km2)", "biofuels_prod_ej", "biogeo_ej",
                                   "coalprod_ej", "gasprod_ej", "hydro_ej", 
                                   "nuclear_ej", "ren_power_ej", "renewables_ej", "solar_ej", "wind_ej")]

ProductionArea$Total <- rowSums(ProductionArea[ , 3:12])
ProductionArea$Renew_Total <- rowSums(ProductionArea[ , 7:12])
ProductionArea$Fossil_Total <- rowSums(ProductionArea[ , 3:6])
ProductionArea$RenewPercent <- (ProductionArea$Renew_Total/ProductionArea$Total) * 100
ProductionArea$FossilPercent <- (ProductionArea$Fossil_Total/ProductionArea$Total) * 100
ProdAreaPer <- ProductionArea[, c("Country", "Area(km2)", "RenewPercent", "FossilPercent")]
names(ProdAreaPer)[2] <- paste("Areakm2")
ProdAreaPer <- melt(ProdAreaPer, id.vars = c("Areakm2", "Country"))
ProdAreaPer$Areakm2 <- as.character(ProdAreaPer$Areakm2)

AreaPlot <- ggplot(ProdAreaPer, aes(x = Areakm2, y = value, fill = variable)) + geom_bar(position = 'stack', stat = 'identity', color = "black") + labs(title = "Energy Production by Area", y = "Percentage %") + labs(col = "Energy") +  
  theme(plot.title = element_text(hjust = 0.5)) + theme(panel.background = element_rect(fill = "light blue",
                                                                                        color = "light blue",
                                                                                        size = 0.5,
                                                                                        linetype = "solid"))
plot(AreaPlot)

```


```{r}
#Looking at at Europe as a hole
#Combine all 10 countries into Europe
EuropeEnergyProd <- Project[, c("Year", "Population", "biofuels_prod_ej", "biogeo_ej", 
"coalprod_ej", "gasprod_ej","nuclear_ej", "hydro_ej", "ren_power_ej", "renewables_ej", 
"solar_ej", "wind_ej")]
EuropeEnergyProd$Population <- as.numeric(EuropeEnergyProd$Population)
EuropeEnergyProd$Total_Prod <- rowSums(EuropeEnergyProd[, 3:12])
EuropeEnergyProd$Renew_Total <- rowSums(EuropeEnergyProd[, 8:12])
EuropeEnergyProd$Fossil_Total <- rowSums(EuropeEnergyProd[, 3:7])

EuropeEnergyProd$RenewPercent <- (EuropeEnergyProd$Renew_Total/EuropeEnergyProd$Total_Prod) * 100
EuropeEnergyProd$FossilPercent <- (EuropeEnergyProd$Fossil_Total/EuropeEnergyProd$Total_Prod) * 100

#Plot total Production in Europe
EuropeEnergyProdTotal <- EuropeEnergyProd[, c("Year", "Total_Prod")]
EuropeEnergyProdTotal <- aggregate(EuropeEnergyProdTotal, by = list(Category = EuropeEnergyProdTotal$Year), FUN = sum)
EuropeEnergyProdTotal <- subset(EuropeEnergyProdTotal, select = -c(Year))
names(EuropeEnergyProdTotal)[1] <- paste("Year")

#Repeat this for the Renew and Fossil Totals
EuropeRenew <- EuropeEnergyProd[, c("Year", "Renew_Total")]
EuropeRenew <- aggregate(EuropeRenew, by = list(Category = EuropeRenew$Year), FUN = sum)
EuropeRenew <- subset(EuropeRenew, select = -c(Year))
names(EuropeRenew)[1] <- paste("Year")

EuropeFossil <- EuropeEnergyProd[, c("Year", "Fossil_Total")]
EuropeFossil <- aggregate(EuropeFossil, by = list(Category = EuropeFossil$Year), FUN = sum)
EuropeFossil <- subset(EuropeFossil, select = -c(Year))
names(EuropeFossil)[1] <- paste("Year")

EuropeEnergyProdTotal$Renew_Total <- EuropeRenew$Renew_Total
EuropeEnergyProdTotal$Fossil_Total <- EuropeFossil$Fossil_Total
#EuropeEnergyProdTotal <- melt(EuropeEnergyProdTotal, id.vars = "Year")


EuropeEnergyProdTotalPlot <- ggplot(EuropeEnergyProdTotal, aes(x = Year)) + geom_line(aes(y = Total_Prod, color = "Total Prod")) + 
  geom_line(aes(y = Renew_Total, color = "Renew")) + 
  geom_line(aes(y = Fossil_Total, color = "Fossils")) + 
  scale_color_manual(values = c("Red", "Green", "Black")) + 
  labs(title = "Total Europe Produced", y = "Energy EJ", col = "Energy") + theme(plot.title = element_text(hjust = 0.5)) + 
  theme(panel.background = element_rect(fill = "light blue", color = "light blue", size = 0.5, linetype = "solid"))


```
# Europe Energy Production
```{r}

plot(EuropeEnergyProdTotalPlot)
```

```{r}
#We will be unable to predict when renewable energy production will over take Fossil fuel energy production 
#energy because the graph above shows this has already taken place.  Therefore, we use the information from 1985 - 2010 
#to train a prediction model and see how accurate it is.

EurEnergylm <- Project[, c("Year", "Population", "biofuels_prod_ej", "biogeo_ej", 
"coalprod_ej", "gasprod_ej","nuclear_ej", "hydro_ej", "ren_power_ej", "renewables_ej", 
"solar_ej", "wind_ej")]
EurEnergylm$Population <- as.numeric(EurEnergylm$Population)
EurEnergylm <- aggregate(EurEnergylm, by = list(Category = EurEnergylm$Year), FUN = sum)
EurEnergylm <- subset(EurEnergylm, select = -c(Year),)
names(EurEnergylm)[1] <- paste("Year")

#Adding Total or overall energy produced, then total by renewable and fossil fuels
EurEnergylm$Total_Prod <- rowSums(EurEnergylm[, 3:12])
EurEnergylm$Renew_Total <- rowSums(EurEnergylm[,8:12])
EurEnergylm$Fossil_Total <- rowSums(EurEnergylm[, 3:7])

#Adding columns of percentages of renewable and fossil fuels produced. 
EurEnergylm$RenewPercent <- (EurEnergylm$Renew_Total/EurEnergylm$Total_Prod) * 100
EurEnergylm$FossilPercent <- (EurEnergylm$Fossil_Total/EurEnergylm$Total_Prod) * 100


Energylm <- EurEnergylm[21:55, ]

Energylmodel <- lm(Energylm$RenewPercent ~ Energylm$biofuels_prod_ej + Energylm$biogeo_ej +
                 Energylm$coalprod_ej + Energylm$gasprod_ej + Energylm$nuclear_ej + Energylm$hydro_ej + 
                 Energylm$ren_power_ej + Energylm$renewables_ej + Energylm$solar_ej + Energylm$wind_ej)
summary(Energylmodel)
```

```{r}

Energylmodel <- lm(Energylm$RenewPercent ~ Energylm$biogeo_ej +Energylm$nuclear_ej + 
                     Energylm$hydro_ej + Energylm$renewables_ej)
summary(Energylmodel)
```

```{r}
#Create Training dataframe
EurEnergylm <- EurEnergylm[21:55, ] #Removing data before 1985.
set.seed(23)
nrows <- nrow(EurEnergylm)
sample_size <- round(0.8*nrows)

#Create random set of numbers
training_index <- sample(1:nrows, size = sample_size, replace = FALSE)

#Create training dataframe of 80%
EnergyTrain <- EurEnergylm[training_index, ]

#Create test dataframe of 20%
EnergyTest <- EurEnergylm[-training_index, ]

library(e1071)

liner_svm <- svm(RenewPercent ~ biofuels_prod_ej + biogeo_ej + coalprod_ej + gasprod_ej + nuclear_ej + hydro_ej + 
                 ren_power_ej + renewables_ej + solar_ej + wind_ej, data = EnergyTrain, type = "eps-regression", kernel = "linear")

liner_svm

pred_Renew <- predict(liner_svm, newdata = EnergyTest)
SVMError <- (EurEnergylm - pred_Renew)

sqrt(mean((EnergyTest$RenewPercent - pred_Renew)^2))

library(Metrics)
rmse(EnergyTest$RenewPercent, pred_Renew)

SVMPlot <- ggplot(data = EurEnergylm, aes(x = Year, y = Total_Prod)) + geom_point(aes(size = RenewPercent)) + 
  labs(title = "SVM Model") + theme(plot.title = element_text(hjust = 0.5)) + theme(panel.background = element_rect(fill = "light blue", color = "light blue", size = 0.5, linetype = "solid"))
plot(SVMPlot)
```


```{r}
#Create a variable for "RenewGreat50"
# If 0 Renew % < 50% or 1 then Renew % > 50%
EurEnergylm$RenewGreat50 <- as.factor(ifelse(EurEnergylm$RenewPercent > 50, 1, 0))

#Rerun training and test data frames.
nrows <- nrow(EurEnergylm)
sample_size <- round(0.8*nrows)
training_index <- sample(1:nrows, size = sample_size, replace = FALSE)
EnergyTrain <- EurEnergylm[training_index, ]
EnergyTest <- EurEnergylm[-training_index, ]

library(kernlab)
modelksvm <- ksvm(RenewGreat50 ~., data = EnergyTrain, kernel = "rbfdot", cost = 50, scale = FALSE)
modelksvmPred <- predict(modelksvm, EurEnergylm, type = "vote")
comptable <- data.frame(EurEnergylm[,18], modelksvmPred[2,])
table(comptable)
```

```{r}
#Calcutaling the error
modelksvmError <- ((32 - 3)/ 36)
modelksvmError
```

```{r}
#Creating the model 
modelksvmPlot <- data.frame(EurEnergylm$Year, EurEnergylm$Total_Prod, modelksvmError)
colnames(modelksvmPlot) <- c("Year", "Total_Prod", "Error")
ModelksvmPlot <- ggplot(modelksvmPlot, aes(x = Year, y = Total_Prod)) + geom_point(aes(size = modelksvmPred[2,], color = "Production"))
ModelksvmPlot <- ModelksvmPlot + labs(title = "KSVM Model", y = "Energy Production") +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(panel.background = element_rect(fill = "light blue",color = "light blue", size = 0.5, linetype = "solid")) +
  scale_color_manual(values = c("Orange")) + labs(col = "Energy Produced")

plot(ModelksvmPlot)
```


