---
title: "Week 2 Homework"
author: "Nick Lichtsinn"
date: "4/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
data(mtcars)
my_mtcars <- mtcars
```

## Step 1: What is the hp
### 1) What is the highest hp
```{r}
max(my_mtcars$hp)
```
### 2) Which car has the highest hp?
```{r}
which.max(my_mtcars$hp)
my_mtcars[31,]
```

## Step 2: Explore mpg
### 3) What is the highest mpg?
```{r}
max(my_mtcars$mpg)
```

### 4) Which car has the highest mpg?
```{r}
which.max(my_mtcars$mpg)
my_mtcars[20,]
```

### 5) Create a sorted dataframe, based on mpg (highest to lowest)
```{r}
mtcarsMPG <- my_mtcars[ order(-my_mtcars$mpg),]
mtcarsMPG
```

##Step 3: Which car has the "best" combination of mpg and hp?
```{r}
mean(my_mtcars$mpg)
mean(my_mtcars$hp)
factor <- mean(my_mtcars$hp)/mean(my_mtcars$mpg)
my_mtcars$mpg_combined <- my_mtcars$mpg*factor*2 + my_mtcars$hp
which.max(my_mtcars$mpg_combined)
my_mtcars[20,]
```

### 6) What logic did you use?
#### In my mind mpg is twice as important as hp so I used the combined number of mpg*2 plus hp.

### 7) Which car?
#### The Toyota Corolla has the highest combined mpg and hp with this logic.

## Step 4: Which car has "best" car combination of mpg and hp, where mpg and hp must be given equal weight?
```{r}
factor <- mean(my_mtcars$hp)/mean(my_mtcars$mpg)
my_mtcars$mpg_combined_equal <- my_mtcars$mpg*factor + my_mtcars$hp
which.max(my_mtcars$mpg_combined_equal)
my_mtcars[31,]
```
#### The Maserati Bora has the "best" combination of mpg and hp when they are given equal weight.