---
title: "Week 2 Lab"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1:
```{r}
data (mtcars)
my_mtcars <- mtcars

```

### Create a new variable for this datafram that represents the engine displacement per cylinder in cubic inches for each vehicle.
```{r}
my_mtcars$EngineDisplacement <- my_mtcars$disp/my_mtcars$cyl
```

### Summarize your new variable using the summary() function.
```{r}
summary(my_mtcars$EngineDisplacement)
```

## Task 2:
### 1. Create three vectors of integers as described above using the c() command to store data reported by group members, with these variable names: Pets, Order, and Siblings.
```{r}
Pets <- c(5,1,3,2,1)
Order <- c(3,2,2,1,1)
Siblings <- c(2,1,1,1,3)
```

### 2. Also create a vector of user ID's for the friends and family members.
```{r}
User_ID <- c("Emily Lorenzen","Nick Lichtsinn","Bomin Powers","Jamie Bigley","Aaron Chadwick")
```

### 3. Bind those four vectors together into a data frame called myFriends.
```{r}
myFriends <- data.frame(Pets,Order,Siblings,User_ID)
```

### 4. Use the appropriate R command to report the structure of your data frame as wel as a summary of the data.
```{r}
str(myFriends)
summary(myFriends)
```

### 5. Use the notation explained on page 33 to list all of the values for each of the variables in the myFriends data frame.
```{r}
myFriends$Pets
myFriends$Order
myFriends$Siblings
myFriends$User_ID
```